Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-04-10 SupportingInformation.Rmd
minor change
testing git

<!--additional details about Cedar creek data-->
Above-ground biomass and percent cover data were obtained from long-term (? or short-term)
biodiversity experiment (E120) conducted in Cedar Creek Ecosystem Science Reserve by 
@Tilman2001; @Tilman2006. In 1994, 168 plots (each 9 m $\times$ 9 m) of 39, 35, 29, 30 and 35 replicates,
were seeded with 1, 2, 4, 8, or 16 perennials, respectively, chosen randomly from a pool of 
18 species (4 species, each, of C4 grasses, C3 grasses, legumes, non-legume forbs; 2 species of woody
plants). All plots received, in total, 10 $gm^{-2}$ of pure live seed in May 1994 and 5 $gm^{-2}$ in May, 1995 
with seed mass divided equally among species. Treatments were maintained by weeding manually 3-4 times a year 
and sometimes selective herbicides were used to set up the monocultures either with only grasses or with only forbs.
We downloaded the data on July, 2018 from Cedar Creek website \url{http://www.cedarcreek.umn.edu/research/experiments/e120} and 
analyzed those [data](https://github.com/sghosh89/BIVAN/tree/master/Data/Ceder_creek_e120) for 6 common years 
(1996-2000, 2007) when both biomass and percent cover data were available. Each plots were annually sampled by clipping 
different locations each year. For each available year, we computed above-ground biomass ($gm^{-2}$) 
and Shannon's biodiversity index (using percent cover data) averaged over the sampled strips/ quadrats taken from each 
of 168 plots.

>>>>

<!--additional details about Cedar creek data, etc.-->
Above-ground biomass and percent cover data were obtained from long-term (? or short-term)
biodiversity experiment (E120) conducted in Cedar Creek Ecosystem Science Reserve by Tilman *et al*.
In 1994, 168 plots (each 9 m $\times$ 9 m) of 39, 35, 29, 30 and 35 replicates,
were seeded with 1, 2, 4, 8, or 16 perennials, respectively, chosen randomly from a pool of 
18 species (4 species, each, of C4 grasses, C3 grasses, legumes, non-legume forbs; 2 species of woody
plants). All plots received, in total, 10 $gm^{-2}$ of pure live seed in May 1994 and 5 $gm^{-2}$ in May, 1995 
with seed mass divided equally among species. Treatments were maintained by weeding manually 3-4 times a year 
and sometimes selective herbicides were used to set up the monocultures either with only grasses or with only forbs.
We downloaded the data on July, 2018 from Cedar Creek website \url{http://www.cedarcreek.umn.edu/research/experiments/e120} and 
analyzed those [data](https://github.com/sghosh89/BIVAN/tree/master/Data/Ceder_creek_e120) for 6 common years 
(1996-2000, 2007) when both biomass and percent cover data were available. Each plots were annually sampled by clipping 
different locations each year. For each available year, we computed above-ground biomass ($gm^{-2}$) 
and Shannon's biodiversity index (using percent cover data) averaged over the sampled strips/ quadrats taken from each 
of 168 plots.
